---
title: "AMA Production Jobs Report"
format: 
  html:
    self-contained: true
    toc: true
    toc-location: left
    toc-depth: 2
execute:
  echo: false
  warning: false
  message: false
lang: en
language:
  code: r
---

# Production & Nonsupervisory Employees

This report visualizes the Adaptive Moving Average (AMA) results for each industry.

```{r setup}
library(here)
source(here::here("plot_ama_job.R"))
#source(here::here("AMA_main.R"))
get_b6_order <- function() {
    c(
        "Total_private",
        "Goods_producing",
        "Mining_logging",
        "Construction",
        "Manufacturing",
        "Durable_goods",
        "Nondurable_goods",
        "Private_service_providing",
        "Trade_transportation_utilities",
        "Wholesale_trade",
        "Retail_trade",
        "Transportation_warehousing",
        "Utilities",
        "Information",
        "Financial_activities",
        "Professional_business_services",
        "Education_health_services",
        "Leisure_hospitality",
        "Other_services"
    )
}
industries <- get_b6_order()
# Only keep those for which a production_jobs RDS file exists
rds_files <- list.files(
    here::here("data/ama_jobs"),
    pattern = "^production_jobs_(.*)_ama\\.rds$",
    full.names = FALSE
)
rds_inds <- gsub("^production_jobs_(.*)_ama\\.rds$", "\\1", rds_files)
industries <- industries[industries %in% rds_inds]
```


## Total private

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Total_private",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Total_private",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Goods producing

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Goods_producing",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Goods_producing",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Mining logging

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Mining_logging",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Mining_logging",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Construction

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Construction",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Construction",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Manufacturing

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Manufacturing",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Manufacturing",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Durable goods

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Durable_goods",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Durable_goods",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Nondurable goods

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Nondurable_goods",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Nondurable_goods",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Private service providing

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Private_service_providing",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Private_service_providing",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Trade transportation utilities

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Trade_transportation_utilities",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Trade_transportation_utilities",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Wholesale trade

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Wholesale_trade",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Wholesale_trade",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Retail trade

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Retail_trade",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Retail_trade",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Transportation warehousing

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Transportation_warehousing",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Transportation_warehousing",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Utilities

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Utilities",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Utilities",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Information

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Information",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Information",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Financial activities

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Financial_activities",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Financial_activities",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Professional business services

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Professional_business_services",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Professional_business_services",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Education health services

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Education_health_services",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Education_health_services",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Leisure hospitality

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Leisure_hospitality",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Leisure_hospitality",
    job_type = "production",
    start_date = "2015-01-01"
)
```

## Other services

### AMA Job Results

```{r}
plot_ama_job(
    industry_name = "Other_services",
    job_type = "production",
    start_date = "2015-01-01"
)
```

### AMA Look-back Window (Right)

```{r}
plot_lookback_right(
    industry_name = "Other_services",
    job_type = "production",
    start_date = "2015-01-01"
)
```

---
